# (PART\*) Part I: Background and Prerequisite {-}

# Introduction {#intro}

## Mutational signatures

Underlying cancer hallmarks are genome instability, which generates the genetic diversity that expedites their acquisition, and inflammation, which fosters multiple hallmark functions [@hanahanHallmarksCancerNext2011]. Cancer genomes typically harbors more than 1,000 mutations in small (e.g., point mutations, short insertions and deletions) and large scale (e.g., copy number variations, rearrangements). Genomic contexts where mutation may accumulate in response to both endogenous processes and exogeneous exposures. In recent years, computational approaches (typically non-negative matrix factorization (NMF)) have been applied to the mutation catalog analysis of human/mouse tumors to detect characteristic mutational patterns, also known as **"mutational signatures"**.


You can label chapter and section titles using `{#label}` after them, e.g., we can reference Chapter \@ref(intro). If you do not manually label them, there will be automatic labels anyway.

Figures and tables with captions will be placed in `figure` and `table` environments, respectively.

```{r nice-fig, fig.cap='Here is a nice figure!', out.width='80%', fig.asp=.75, fig.align='center'}
par(mar = c(4, 4, .1, .1))
plot(pressure, type = 'b', pch = 19)
```

Reference a figure by its code chunk label with the `fig:` prefix, e.g., see Figure \@ref(fig:nice-fig). Similarly, you can reference tables generated from `knitr::kable()`, e.g., see Table \@ref(tab:nice-tab).

```{r nice-tab, tidy=FALSE}
knitr::kable(
  head(iris, 20), caption = 'Here is a nice table!',
  booktabs = TRUE
)
```

You can write citations, too. For example, we are using the **bookdown** package [@R-bookdown] in this sample book, which was built on top of R Markdown and **knitr** [@xie2015].


# (PART\*) Part II: Workflows {-}

# (PART\*) Part III: Miscellaneous topics {-}

# (APPENDIX) Appendix {-}
