# Package prerequisite and installation 

## Package prerequisite

All R package dependencies of **sigminer** can be checked at [specific fields of *DESCRIPTION* file](https://github.com/ShixiangWang/sigminer/blob/4a10d0811cb3bcb02dbbff73ed1c218954bf9b42/DESCRIPTION#L45-L100).
Of note, unlike common R package, many key features of **sigminer** are only available when the suggested packages are installed.
Most of them are from [*Bioconductor*](http://bioconductor.org/), so R package **BiocManager** must be installed
before installing **sigminer**. You have to use **BiocManager** instead of `install.packages()` to install **sigminer**.
If you want to handle other reference genome data except `hg19`, e.g., for `hg38`, you also have to install *Bioconductor*
package **BSgenome.Hsapiens.UCSC.hg38** before/after installing **sigminer**.

## Package installation

The stable release version of **sigminer** package can be installed from the CRAN:

```{r, eval=FALSE}
install.packages("BiocManager")
BiocManager::install("sigminer", dependencies = TRUE)
```

Set `dependencies = TRUE` is recommended because many packages are required for accessing full features provided by **sigminer** (we described this in previous section).
The development version of **sigminer** package can be installed from Github or Gitee after installing CRAN version **sigminer**:

```{r eval=FALSE}
install.packages("remotes")
# From GitHub
remotes::install_github("ShixiangWang/sigminer", dependencies = TRUE)
# From Gitee
remotes::install_git("https://gitee.com/ShixiangWang/sigminer", dependencies = TRUE)
```

If you see notification of package update, please keep this package up to date.


The **sigminer** is also available in Conda *forge* channel. If you are using Conda,
you can install **sigminer** with:


```R
# Please note version number of the bioconda release

# You can install an individual environment firstly with
# conda create -n sigminer
# conda activate sigminer
conda install -c bioconda -c conda-forge r-sigminer
```

## Package loading 

To load package, run:

```{r}
library(sigminer)
```

More info about **sigminer** can be given as: 

```{r, echo = TRUE}
hello()
```

## Package references

All datasets/functions are well organized and documented at [package *referrence* list](https://shixiangwang.github.io/sigminer/reference/index.html).
For checking usage of a specific function `fun`, you can also run `?fun` in your R console.
For example, to see usage `read_copynumber()`

```R
library(sigminer)
?read_copynumber
```

