# (PART\*) Part III: Miscellaneous topics {-}

# Universal analysis {#universal-analysis}

## Association analysis and visualization

### General numeric association

For general numeric association, you can use `show_cor()` function.

```{r}
data("mtcars")
p1 <- show_cor(mtcars)
p2 <- show_cor(mtcars,
               x_vars = colnames(mtcars)[1:4],
               y_vars = colnames(mtcars)[5:8])
p3 <- show_cor(mtcars, vis_method = "circle", p_adj = "fdr")
p1
p1$cor
p2
p3
```

### Comprehensive association

For comprehensive association analysis including both continuous and categorical variables,
there are several functions available in **sigminer**:

- `get_sig_feature_association()`.
- `get_tidy_association()`.
- `show_sig_feature_corrplot()`.

Currently, I haven't provided a proper example dataset for showing usage of all functions above (please read their documentation), here only the tidy dataset from our study [@wang2021copy] is given to show the plot function.

```{r, error=TRUE, fig.height=7, fig.width=6}
# The data is generated from Wang, Shixiang et al.
load(system.file("extdata", "asso_data.RData",
  package = "sigminer", mustWork = TRUE
))
p <- show_sig_feature_corrplot(tidy_data.seqz.feature, p_val = 0.05)
p
```


## Group Analysis and Visualization

Group analysis is a common task in cancer study. **Sigminer** supports dividing samples into multiple groups and comparing genotype/phenotype feature measures.

### Group Generation 

There are multiple methods to generate groups, including 'consensus' (default, can be only used by result from `sig_extract()`), 'k-means' etc. After determining groups, **sigminer** will assign each group to a signature with maximum fraction. We may say a group is `Sig_x` enriched.

```{r}
data("simulated_catalogs")
mt_sig <- sig_extract(t(simulated_catalogs$set1), n_sig = 10, nrun = 3)
```

```{r, message=TRUE}
mt_grps <- get_groups(mt_sig, method = "consensus", match_consensus = TRUE)
head(mt_grps)
```

The returned sample orders match sample orders in clustered consensus matrix.

```{r}
show_sig_consensusmap(mt_sig)
```


Sometimes, the mapping between groups and enriched signatures may not right. Users should check it and even correct it manually.


```{r}
attr(mt_grps, "map_table")
```


### Group Comparison Analysis 

```{r}
load(system.file("extdata", "toy_copynumber_signature_by_W.RData",
  package = "sigminer", mustWork = TRUE
))
# Assign samples to clusters
groups <- get_groups(sig, method = "k-means")
set.seed(1234)
groups$prob <- rnorm(10)
groups$new_group <- sample(c("1", "2", "3", "4", NA), size = nrow(groups), replace = TRUE)
# Compare groups (filter NAs for categorical coloumns)
groups.cmp <- get_group_comparison(groups[, -1],
  col_group = "group",
  cols_to_compare = c("prob", "new_group"),
  type = c("co", "ca"), verbose = TRUE
)
# Compare groups (Set NAs of categorical columns to 'Rest')
groups.cmp2 <- get_group_comparison(groups[, -1],
  col_group = "group",
  cols_to_compare = c("prob", "new_group"),
  type = c("co", "ca"), NAs = "Rest", verbose = TRUE
)
```


### Group Visualization 

```{r}
ggcomp <- show_group_comparison(groups.cmp2)
ggcomp$co_comb
ggcomp$ca_comb
```


# Subtype prediction {#subtype-prediction}

To expand the power of signatures to clinical application, based on signature activity, we can go further build neutral network model prediction model with [*keras*](https://keras.io/). This feature is implemented in sigminer’s child package [**sigminer.prediction**](https://github.com/ShixiangWang/sigminer.prediction).

If you are studying copy number signatures of prostate cancer, you can directly use the trained model, the usage has been described in the
[*README* file](https://github.com/ShixiangWang/sigminer.prediction/blob/master/README.md).

For other situations, you can reuse the functions [`modeling_and_fitting()`](https://github.com/ShixiangWang/sigminer.prediction/blob/master/R/modeling_and_fitting.R)
and [`batch_modeling_and_fitting()`](https://github.com/ShixiangWang/sigminer.prediction/blob/master/R/batch_modeling_and_fitting.R) (for batch processing) for building models.

# Sigflow pipeline {#sigflow}

[**Sigflow**](https://github.com/ShixiangWang/sigflow) provides useful mutational signature analysis workflows based on R package **sigminer**. It can auto-extract mutational signatures, fit mutation data to COSMIC reference signatures (SBS/DBS/INDEL) and run bootstrapping analysis for signature fitting.

For full documentation, please read Sigflow [*README*](https://github.com/ShixiangWang/sigflow).

## Cancer type specific signature index database

Signature fitting analysis may befit from directly specifying known signatures identified in a cancer type. We collect such information and provide the following data tables.

```{r}
db1 <- system.file("extdata", "cosmic2_record_by_cancer.rds", package = "sigminer")
db1 <- readRDS(db1)
colnames(db1) <- c("Cancer type", "Signature Index")
db2 <- system.file("extdata", "signature_record_by_cancer.rds", package = "sigminer")
db2 <- readRDS(db2)
colnames(db2) <- c("Cancer type", "Cohort", "Sequencing strategy",
                   "SBS signature index",
                   "DBS signature index",
                   "ID signature index")
```

```{r}
DT::datatable(db1, caption = "Data source: https://cancer.sanger.ac.uk/signatures_v2/matrix.png")
```

> Note, set `sig_db` to 'legacy' (the default) in `sig_fit()` family functions.

```{r}
DT::datatable(db2[, c(1:3, 4)], caption = "Data source: Alexandrov et al. https://www.nature.com/articles/s41586-020-1943-3")
```

```{r}
DT::datatable(db2[, c(1:3, 5)], caption = "Data source: Alexandrov et al. https://www.nature.com/articles/s41586-020-1943-3")
```

```{r}
DT::datatable(db2[, c(1:3, 6)], caption = "Data source: Alexandrov et al. https://www.nature.com/articles/s41586-020-1943-3")
```

# Datasets {#datasets}

## Reference annotation 

**sigminer** stores many reference annotation datasets for internal calculation. It can be exported for other usage either by `data()` or `get_genome_annotation()`.

Currently, there are the following datasets:

- `centromeres.hg19`
- `centromeres.hg38`
- `chromsize.hg19`
- `chromsize.hg38`
- `cytobands.hg19`
- `cytobands.hg38`

An example is given as below:

```{r}
data("centromeres.hg19")
head(centromeres.hg19)
```


`get_genome_annotation()` can better control the returned `data.frame`.

```{r}
get_genome_annotation(data_type = "chr_size",
                      chrs = c("chr1", "chr10", "chr20"),
                      genome_build = "hg19")
```


More see `?get_genome_annotation`.

## Copy number components setting 

Dataset `CN.features` is a predefined component data table for identifying copy number signatures by method "Wang".
Users can define a custom table with similar structure and pass it to function like `sig_tally()`.

Detail about how to generate this dataset can be viewed at <https://github.com/ShixiangWang/sigminer/blob/master/data-raw/CN-features.R>.

```{r}
CN.features
```

# SBS signature conversion {#convert}

Converts signatures between two representations relative to different sets of mutational opportunities. Currently, only SBS signature is supported.

```{r, fig.width=12}
# Load SBS signature
load(system.file("extdata", "toy_mutational_signature.RData",
  package = "sigminer", mustWork = TRUE
))
# Exome-relative to Genome-relative
sig_converted <- sig_convert(sig2,
  from = "human-exome",
  to = "human-genome"
)
sig_converted
show_sig_profile(sig2, style = "cosmic")
show_sig_profile(sig_converted, style = "cosmic")
```


# (APPENDIX) Appendix {-}
